R Notebook

### 2021-09-13 documentation_and_analysis/draftbook.Rmd
EV Geospatial Working

```{r}
library(tidyverse)
library(readODS)
library(httr)
```

```{r}
read_ods("Downloads/electric-vehicle-charging-device-statistics-july-2021.ods")
```

```{r}
APE <- read_ods("Downloads/APE_site_data_tables.ods", sheet = 2)
```

```{r}
NO2 <- read_ods("Downloads/NO2_tables.ods")
```

@@

```{r}

```

@@

>>>>

```{r}
library(tidyverse)
library(janitor)
library(readODS)
library(httr)
library(here)
library(data.table)
library(sf)
library(leaflet)
```

```{r}
read_ods(here("raw_data/electric-vehicle-charging-device-statistics-june-2021.ods"))
```

```{r}
getwd()
```

```{r}
APE <- read_ods("raw_data/APE_site_data_tables.ods", sheet = 2)
```

```{r}
NO2 <- read_ods("raw_data/NO2_tables.ods")
```

@@

@@

```{r}
air_pollution <- GET("https://uk-air.defra.gov.uk/data/sos/service?service=AQD&version=1.0.0&request=GetObservation&temporalFilter=om:phenomenonTime,After,yyyy-mm-ddT00:00:00.000Z") 
```

```{r}
air_pollution <- rbindlist(air_pollution$content, fill = TRUE) 
```

```{r}
air_pollution <- unnest(air_pollution)
```

# How many electric vehicles are on the road across the UK?

```{r}
# Reading in and skipping first 5 rows
uk_ev <- read_ods(here("raw_data/ev_by_la.ods"), skip = 5)
# Making row 1 the variable name
names(uk_ev) <- uk_ev[1,] 
# Removing row 1 
uk_ev <- uk_ev[-1,] %>% 
  clean_names()
```

```{r}
# loading in shape file 
uk_shape_file <- st_read(here("raw_data/Local_Authority_Districts__April_2019__UK_BFE_v2-shp/Local_Authority_Districts__April_2019__UK_BFE_v2.shp")) %>%
  clean_names() %>% 
  st_simplify(dTolerance = 1000) %>%
  st_transform("+proj=longlat +datum=WGS84") %>% 
  select(lad19cd, long, lat, geometry)
```

```{r}
# Joining uk_ev + shape file 
uk_ev_map <- uk_ev %>% 
  left_join(uk_shape_file, by = c("ons_la_code_apr_2019" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(x2021_q1:x2011_q4), as.numeric))
```

```{r}
    pal <- colorBin("Greens", domain = uk_ev_map$x2021_q1, bins = 10)

    uk_ev_map_labels <- sprintf(
      uk_ev_map$region_local_authority_apr_2019_3, uk_ev_map$x2021_q1)
```

```{r}
leaflet(uk_ev_map) %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(data = uk_ev_map$geometry,
             # fillColor = ~pal(x2021_q1),
              weight = 0.5,
              opacity = 0.9, 
              color = "green",
              fillOpacity = 0,
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                      bringToFront = TRUE),
              label = uk_ev_map_labels,
                  labelOptions = labelOptions(
                    style = list("font-weight" = "normal", padding = "3px 8px"),
                    textsize = "15px",
                    direction = "auto")) %>% 
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
                position = "bottomright")
```

```{r}
uk_ev_map$x2021_q1 %>% 
  range()
```
